### 2017-01-11 README.Rmd
create README-figs dir for README figs

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

@@

There are two main commands in the `visdat` package:

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-figs/README-"
)

@@

There are two main commands in the `visdat` package: 
- `vis_dat()` 
- `vis_miss()`
